Species motif participation provides unique information about species risk of extinction

### 2023-05-12 manuscript/supplement_motifs.tex
Updates from Overleaf

    Appendices S1-S3 provide supplemental methods, while appendices S4-S6 provide supplemental results.

@@

@@

            \begin{itemize}
                \item Details on functional response of consumers
                \item Contains Eqn. S1
            \end{itemize}

            \begin{itemize}
            \item Construction of simulated networks
            \item Filtering of biologically unrealistic networks 
            \item Conversion of networks to acyclic form
            \item Comparison of empirical and simulated networks
            \item Contains Fig. S1
            \end{itemize}

@@

            \begin{itemize}
                \item Persistence and other network properties (Eqn. S2-3)
                \item Motif participation, profiles and network properties (Eqn. S4-6)
            \end{itemize}

        \item Results: species motif participation 
            \begin{itemize}
                \item Supplemental results relating species motif participation to persistence and to other network properties (S, C, in-degree, STL)
                \item Contains Table S1-2
                \item Contains Fig. S2
            \end{itemize}

        \item Results: persistence and other network properties

            \begin{itemize}
                \item Identifying relationships between persistence and network size, connectance, in-degree, and STL to provide context for motif relationships.
                \item Contains Tables S3-4
                \item Contains Fig. S3
            \end{itemize}

@@

            \begin{itemize}
                \item Describes GLMs summarising how the relationship between motif participation and persistence varies over S and C, to complement the within-netowrk results presented in the main text
                \item Contains Fig. S4
            \end{itemize}

        \item Results: network motif profiles

            \begin{itemize}
                \item Relating motif profiles to persistence (see main text for equation, figure) and to network size and connectance
                \item Contains Tables S5-6
            \end{itemize}

@@

            \begin{itemize}
                \item Contains Table S7
            \end{itemize}

@@

\linenumbers
\section{Calculating persistence}

@@

\section{Network creation}

    \subsection*{Generation of simulated networks}

    \subsection*{Filtering of biologically unrealistic networks}

    \subsection*{Conversion of networks to acyclic form}

    \subsection*{Comparison of empirical and simulated networks}

    \subsubsection*{Comparing motif profiles}

    \subsubsection*{Comparing motif participation}

@@

    \textbf{Persistence, degree, and trophic level}

@@

    \textbf{Motif participation, profiles and other network properties}

@@

\section{Results: motif participation}

    % \begin{figure}[hb!]
    %     \centering
    %     \includegraphics[width=.9\textwidth]{figures/participation_vs_SC.eps}
    %     \caption{The proportion of each motif in consumer's participation vectors varied with connectance, network size, and their interaction (except for apparent competition). We show relationships for the smallest and largest values of network size (S) and connectance (C).}
    %     \label{fig:roles_vs_SC}
    % \end{figure}

\section{Results: persistence and other network properties}

    % \begin{figure}[ht!]
    %     \centering
    %     \includegraphics[width=0.9\textwidth]{figures/persistence_vs_SC_lm.eps}
    %     \caption{Persistence decreased strongly with increasing probability of disturbance to basal resources and decreased slightly, but significantly, with increasing connectance.}
    %     \label{fig:lm_CS}
    % \end{figure}

@@

@@

@@

>>>>

    Appendices S1-S4 provide supplemental methods, while appendices S4-S7 provide supplemental results.

@@

            \begin{itemize}
            \item Construction of simulated networks
            \item Filtering of biologically unrealistic networks 
            \item Conversion of networks to acyclic form
            \item Comparison of empirical and simulated networks (Fig. S1)
            \end{itemize}

@@

            \begin{itemize}
                \item Details on functional response of consumers (Eqn. S1)
            \end{itemize}

@@

            \begin{itemize}
                \item Describes GLMs relating persistence and other network properties (Eqn. S2-3) and GLMs relating motif participation, profiles and network properties (Eqn. S4-6)
            \end{itemize}

@@

            \begin{itemize}
                \item Describes GLMs summarising how the relationship between motif participation and persistence varies over S and C, to complement the within-network results presented in the main text (Eqn. S7)
                \item Plots of these GLMs for each motif (Figs. S2-5)
            \end{itemize}

        \item Results: species motif participation 
            \begin{itemize}
                \item Supplemental results relating species motif participation to persistence and to other network properties (S, C, in-degree, STL)
                \item Table S1-2l; Fig. S6
            \end{itemize}

        \item Supplemental results: persistence and other network properties

            \begin{itemize}
                \item Supplemental results identifying relationships between persistence and network size, connectance, in-degree, and STL to provide context for motif relationships (Tables S3-4).
                \item Also relating average persistence to network motif profiles (Table S5)
            \end{itemize}

        \item Supplemental results: network motif profiles

            \begin{itemize}
                \item Relating motif profiles  to network size and connectance (Table S6)
            \end{itemize}

@@

            \begin{itemize}
                \item Definitions of network terminology used in main text (Table S7)
            \end{itemize}

@@

\linenumbers
\section{Network creation}

    \subsection{Generation of simulated networks}

    \subsection{Filtering of biologically unrealistic networks}

    \subsection{Conversion of networks to acyclic form}

    \subsection{Comparison of empirical and simulated networks}

    \subsubsection{Comparing motif profiles}

    \subsubsection{Comparing motif participation}

\section{Calculating persistence}

@@

@@

    \subsection{Persistence, degree, and trophic level}

@@

    \subsection{Motif participation, profiles and other network properties}

@@

@@

    \subsection{Supplemental methods}

@@

    \subsection{Supplemental results}

@@

\section{Supplemental results: motif participation}

    \begin{figure}[ht!]
        \centering
        \includegraphics[width=\textwidth]{figures/roles_vs_SC_all.eps}
        \caption{The proportion of each motif in consumer's participation vectors varied with connectance, network size, and their interaction (except for apparent competition).}
        \label{fig:motifs_vs_TL_and_deg}
    \end{figure}

\section{Supplemental results: persistence and other network properties}

    \subsection{Persistence and non-motif measures}
    % \begin{figure}[ht!]
    %     \centering
    %     \includegraphics[width=0.9\textwidth]{figures/persistence_vs_SC_lm.eps}
    %     \caption{Persistence decreased strongly with increasing probability of disturbance to basal resources and decreased slightly, but significantly, with increasing connectance.}
    %     \label{fig:lm_CS}
    % \end{figure}
